\section{Resources}

\note{
As for 2019 call, this section is filled online.\\
% 
\textbf{It is strongly recommended to use the Part B2 budget table
template} to facilitate the assessment of resources by the panels.
State the amount of funding considered necessary to fulfil t he
research objectives. The project cost estimation should be as
accurate as possible. The requested budget should be fully
justified and in proportion to the actual needs. The evaluation
panels assess the estimated costs carefully; \textbf{unjustified
budgets will be consequently reduced}. Specify your commitment to
the project and how much time you are willing to devote to the
proposed project (You are expected to spend as a minimum 50\% for
STG and 40\% for COG of your working time on the ERC project).
Describe the size and nature of the team, indicating, where
appropriate, the key team members and their roles. The
participation of team members engaged by other host institutions
should be justified and in relation to the additional financial
cost this may impose. When estimating your personnel costs take
into account the dedicated working time to run the project.
Specify any existing resources that will contribute to the
project. Describe other necessary resources, such as
infrastructure and equipment. Include a short technical
description of any requested equipment, why you need it and how
much you plan to use it for the project. Please include a
realistic estimation of the costs for Open Access to project
outputs. Costs for providing immediate Open Access to publications
(article processing charges/book processing charges) are eligible
if they are incurred during the lifetime of the project.
}
